|

### 2021-03-21 documentation/readme.Rmd
Various fixes

`{britpol}` is an `R` package that makes analysing British political data quick and simple. It contains two pre-formatted datasets, plus a host of useful functions. The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia. The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties from `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

@@

As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain. They hold a lead over the `r txt_dta$party[2]` of around `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.

>>>>

The `{britpol}` package makes analysing British political data quick and simple. It contains two pre-formatted datasets, plus a host of useful functions. The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia. The second, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties from `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

@@

The `pollbasepro` data suggest that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain. They hold a lead over the `r txt_dta$party[2]` of around `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.

### 2021-03-21 documentation/userguide.Rmd
Various fixes

data("pollbase")
data("pollbasepro")

# Load imputed sample sizes

@@

timeline <-
  load_timeline() %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

# Load correlation models

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))

@@

make_table(pollbase)

@@

make_table(pollbasepro)

@@

To validate our estimates, we compare them against raw polling data from Jennings and Wlezien's "Timeline of Elections" dataset [-@jennings2016a]. These data contain `r format(nrow(timeline[timeline$party == 1, ]), big.mark = ",")` polls from Britain between `r str_remove(format(min(as_date(timeline$date)), "%d %B %Y"), "^0")` and `r str_remove(format(max(as_date(timeline$date)), "%d %B %Y"), "^0")`. Given that the data we use to produce our estimates are so comprehensive, it is likely that most polls appear in both datasets. Still, the Timeline data provide a good test as Jennings and Wlezien compiled them independently. As figure \@ref(fig:val-plot) shows, our estimates are well validated. Correlations between the two series are strong and positive, as we would expect. Their mean absolute error (MAE) and root-mean-square error (RMSE) are also low in all cases. The Conservatives showed a correlation of `r in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_con$data$con_est*100, cor_con$data$vote*100), 2), " percentage points")`, and an RMSE of `r round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)`; Labour, a correlation of `r in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lab$data$lab_est*100, cor_lab$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)`; and the Liberals, a correlation of `r in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lib$data$lib_est*100, cor_lib$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)`.

@@

save_info(path = here("sessions", "007_codebook.txt"))

>>>>

data("pollbase")
data("pollbasepro")
data("samplesizes")

# Load correlations

@@

timeline <-
  britpol:::load_timeline() %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

@@

britpol:::make_table(pollbase)

@@

britpol:::make_table(pollbasepro)

@@

To validate our estimates, we compare them against raw polling data from Jennings and Wlezien's "Timeline of Elections" dataset [-@jennings2016a]. These data contain `r format(nrow(timeline[timeline$party == 1, ]), big.mark = ",")` polls from Britain between `r str_remove(format(min(as_date(timeline$date)), "%d %B %Y"), "^0")` and `r str_remove(format(max(as_date(timeline$date)), "%d %B %Y"), "^0")`. Given that the data we use to produce our estimates are so comprehensive, it is likely that most polls appear in both datasets. Still, the Timeline data provide a good test as Jennings and Wlezien compiled them independently. As figure \@ref(fig:val-plot) shows, our estimates are well validated. Correlations between the two series are strong and positive, as we would expect. Their mean absolute error (MAE) and root-mean-square error (RMSE) are also low in all cases. The Conservatives showed a correlation of `r britpol:::in_text(cor_mods$tl_con*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_con, 2), " percentage points")`, and an RMSE of `r round(cor_mods$rmse_con, 2)`; Labour, a correlation of `r britpol:::in_text(cor_mods$tl_lab*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_lab, 2), " points")`, and an RMSE of `r round(cor_mods$rmse_lab, 2)`; and the Liberals, a correlation of `r britpol:::in_text(cor_mods$tl_lib*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_lib, 2), " points")`, and an RMSE of `r round(cor_mods$rmse_lib, 2)`.

@@

britpol:::save_info(path = here("sessions", "008_codebook.txt"))
